Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-10-03 response-reviewers-2.tex

\vspace{0.5cm}

% ********** comienzo del texto  *******************

{\bf Response to reviewers' comments}

We are very grateful to the reviewers for their kind comments. We have rewritten
the paper quite extensively, incorporating requested changes, but also
attempting to give another angle that makes this paper apart from what was
already published in another (hidden for double blind review).

### 2023-01-06 edubots_surveys.Rnw
Fix grammar error and typos

\textcolor{blue}{New technologies are being introduced and widely adopted into the classroom in the last years. However, in order to be successful, their application 
will require (many) extra work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will 
get a higher engagement to the subject, which is usually the main objective. Even if several technologies are already in use inside the classroom, there is still room for adopting others.
Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this, 
asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology}.

>>>>

\textcolor{blue}{In recent years, new technologies are being widely adopted and introduced into the classroom. However, in order to be successful, their application 
will require additional work and training for the teacher, as well as for the students. Thus, both of them will acquire new skills and, potentially, pupils will be more 
engaged to the subject, which is usually the main objective. Even if several technologies are already in use in the classroom, there is still room for adopting new others.
Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Asking and analyzing users' 
opinions with regard to this scenario will help reaping the expected benefits of the technology}.
